---
output: github_document
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# new.name
An R package that uses the babynames and unisex datasets to help users choose new names using criteria having to do with the letters in the name (e.g., a beginning letter) and/or a year the name was used in the United States at least five times. More name sets to be added!



## Purpose
The new.name package includes functions and datasets to help people choose a new name. This package aims to use string manipulation and data wrangling to find subsets of names based on certain characteristics. 
Perhaps you want to choose a new name that starts with certain letters or maybe you want something random. 


## Target
This package is intended for anyone who needs help deciding a new name. 

## Installation

You can install the development version of new.name like so:

``` r
devtools::install_github("mars-ikeda/new.name")
```

## Example

Find popular names during a year(y) that starts with a letter(x)

```{r}

```

## Example 
Find a random name

```{r random name}
RandomName()
```
